\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-25 paper.qmd
Updated Figure 16

error_plot_mnist <- error_df |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2, 
             color = type, 
             group = ID)) +
  geom_point(alpha=0.5, 
             size = 0.1) +
  interior_annotation("b", sc_ltr_pos_mnist)
```

<!--bin1 = 22, bin2 = 17, b = 374, non_empty = 140-->
```{r}
#| echo: false
#| fig-cap: "(a) Model generated in $2\\text{-}D$, and (b) $p\\text{-}D$ model error in $2\\text{-}D$. The $2\\text{-}D$ model shows a non-linear continuous structure. Most low $p\\text{-}D$ model errors are distributed along the lower edge of the $2\\text{-}D$ structure, while most high p-D model errors are concentrated along the upper edge."
#| label: fig-model-mnist
#| fig-pos: H

trimesh_removed_mnist + error_plot_mnist + 
  plot_layout(guides='collect', ncol=2) &
  theme(legend.position='bottom')
```

>>>>

error_plot_mnist <- error_df |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2, 
             color = type, 
             group = ID)) +
  geom_point(alpha=0.5, 
             size = 0.1) #+
  #interior_annotation("b", sc_ltr_pos_mnist)
```

<!--bin1 = 22, bin2 = 17, b = 374, non_empty = 140-->
```{r}
#| echo: false
#| fig-cap: "$10\\text{-}D$ model error in $2\\text{-}D$. The $2\\text{-}D$ model shows a non-linear continuous structure. Most low $10\\text{-}D$ model errors are distributed along the lower edge of the $2\\text{-}D$ structure, while most large $10\\text{-}D$ model errors are concentrated along the upper edge."
#| label: fig-model-mnist
#| fig-pos: H
#| out-height: 22%

error_plot_mnist + 
  plot_layout(guides='collect') &
  theme(legend.position='bottom')
```

### 2024-08-25 paper.tex
Updated Figure 16

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-model-mnist-1.pdf}

@@

\caption{\label{fig-model-mnist}(a) Model generated in \(2\text{-}D\),
and (b) \(p\text{-}D\) model error in \(2\text{-}D\). The \(2\text{-}D\)
model shows a non-linear continuous structure. Most low \(p\text{-}D\)
model errors are distributed along the lower edge of the \(2\text{-}D\)
structure, while most high p-D model errors are concentrated along the
upper edge.}

>>>>

\includegraphics[width=1\textwidth,height=0.22\textheight]{paper_files/figure-pdf/fig-model-mnist-1.pdf}

@@

\caption{\label{fig-model-mnist}\(10\text{-}D\) model error in
\(2\text{-}D\). The \(2\text{-}D\) model shows a non-linear continuous
structure. Most low \(10\text{-}D\) model errors are distributed along
the lower edge of the \(2\text{-}D\) structure, while most large
\(10\text{-}D\) model errors are concentrated along the upper edge.}
